### 2015-04-20 paper.tex
Add test parameters section
Add todo list

@@

@@

>>>>

% To-do notes
\usepackage{todonotes}

@@

\listoftodos

@@

\subsection*{Test parameters}

Data collection runs were separated into individual tows, for which all
independent variables---tow speed, tip speed ratio, velocity probe
position---were held constant. These runs were grouped into logical test matrix
``sections,'' in which typically a single independent variable was varied.

\todo[inline]{Add all test matrix sections and their descriptions here.}
